Counterexamples in Mathematical Relations

### 2024-10-10 Relations/RewritingQs.tex
ARS progress

@@

@@

   \emph{Note.}  This seems to require the most classical assumptions:
   $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
   Markov's principle, etc.
\end{enumerate}

>>>>

\usepackage{xcolor}

@@

\section{2024.10.10}

\begin{itemize}
  \item Look at restricting WFmin to $\lnot\lnot$-closed predicates
  \item Status of important hypotheses:
    \begin{itemize}
      \item Deciding whether a given element $x$ reduces to a given element $y$
      (Is $R$ itself decidable?)
      \item Deciding whether a given element $x$ reduces to some element $y$
      (Is being an $R$-normal form decidable?)

      {\textcolor{red}{This is needed to show that SN $\Rightarrow$ WN.}}

      \item If a given element $x$ is \emph{not} a normal form,
      exhibiting some element $y$ that it reduces to.
      (This is related to DeMorgan/Markov/etc. properties that came up in WF file.)

      \item Does UN-lemma \emph{require} the decidability assumption?
    \end{itemize}
  \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
  for example,
  \begin{itemize}
    \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
    \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
  \end{itemize}
  \item When time permits, uniformize the notation (variable names, etc.) to the extent possible.
\end{itemize}

\section{2024.09.19}

TODO item: Compile a list of counterexamples

@@

   \emph{Note.}  This seems to require the most classical assumptions:
   $\lnot\lnot$-closure of $\phi$, relativized De Morgan law,
   Markov's principle, etc.

   \item (2024.10.10) Is being $R$-WN inductive?
   \item (2024.10.10) Does $R$ being finitely branching imply
   that, for an inductive $\phi$, if $\lnot \phi(x)$ then
   $\exists y. Rxy \land \lnot \phi(y)$?

\end{enumerate}
